Interference Transform: Estimating the frequency and phase of low resolution samples

### 2020-05-18 Papers/01_interf_transf/Interference Transform.tex
fixed formatting issues with plotly

  \begin{figure}[h!]
    \centering
      \includegraphics[width=0.8\linewidth]{images/01ContinuousVsDiscrete}
    \caption{Discrete samples (black points) from a continuous wave (grey line). Note that the amplitude is also truncated}
    \label{fig:ContinuousVsDiscrete}
  \end{figure}

  Thus, we have:
  $ W[i] \in \mathbb{R} \forall i \in \mathbb{N}, 0 \le i < n $,
  $ S(t) \in \mathbb{R} \forall t \in \mathbb{R}, 0 \le t < t_f $ where $ t_f=n / \textrm{fps} $

>>>>

  \begin{figure}[h!]
    \centering
      \includegraphics[width=0.8\linewidth]{images/01ContinuousVsDiscrete.eps}
    \caption{Discrete samples (black points) from a continuous wave (grey line). Note that the amplitude is also truncated}
    \label{fig:ContinuousVsDiscrete}
  \end{figure}

  Thus, we have:
  $ W[i] \in \mathbb{R} \  \forall \  i \in \mathbb{N}, 0 \le i < n $
  $ S(t) \in \mathbb{R} \  \forall \  t \in \mathbb{R}, 0 \le t < t_f $ where $ t_f=\frac{n}{\textrm{fps}} $.

  The relationship is better illustrated comparing two equivalent simple sinusoids, being one continuous and its discrete counterpart. Those can be described, respectively as 
  $$ S(t) = a \cos \left( \phi + 2 \pi \mathcal{F} t \right) $$
  and
  $$ W[i] = a \cos \left( \phi + 2 \pi f \frac{i}{n} \right) $$
  where:

  $ \mathcal{F} \in \mathbb{R}^+ $, absolute frequency of the continuous wave in Hz;

  $ f \in \mathbb{R}^+ $, relative frequency of the discrete wave in cycles per $n$ samples;

  $ f = \frac{n}{\textrm{fps}} \mathcal{F} $;

  $ i = t \  \textrm{fps}, i \in \mathbb{N} $, frame number;

  $ t \in \mathbb{R} $, time in seconds;

  $ n \in \mathbb{N} $, number os discrete samples;

  $ 0 \le \frac{i}{n} < 1 $;

  $ a \in \mathbb{R}^+ $, amplitude;

  $ \phi \in \mathbb{R}^+, 0 \le \phi < 2 \pi $, phase;

  \begin{figure}[h!]
    \centering
      \includegraphics[width=0.8\linewidth]{images/01ContinuousVsDiscreteSinusoid}
    \caption{Continuous sinusoid (grey line) and the correspondent Discrete sinusoid (black points) illustrating the correspondence between frames i and time t}
    \label{fig:ContinuousVsDiscreteSinusoid}
  \end{figure}

  \begin{figure}[h!]
    \centering
      \includegraphics[width=0.8\linewidth]{images/03OptSinusoids}
    \caption{Sinusoids with maximum coinciding with sampled points i=3 and i=28 }
    \label{fig:OptSinusoids}
  \end{figure}
